%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}
\usepackage{xcolor}

% Define the blue color for hyperlinks
\definecolor{linkcolor}{rgb}{0,0,0.5}

% Configure hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    citecolor=linkcolor
}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    {\Huge\bfseries Phil Palmer} \\ \vspace{3pt}
    % mail to
    \href{mailto:pp502@cam.ac.uk}{\color{teal}pp502@cam.ac.uk} \\
    % \small born 26 August 1997 $|$ British $|$ 
    \href{https://github.com/PhilPalmer}{\color{teal}GitHub} $|$ \href{https://scholar.google.com/citations?user=VMrmNJcAAAAJ}{\color{teal}Google Scholar} $|$ \href{https://uk.linkedin.com/in/phil-palmer}{\color{teal}LinkedIn} $|$ \href{https://philpalmer.github.io/blog/}{\color{teal}Website} $|$  +44 7531 445 903 \\
\end{center}



%----------- EDUCATION -----------

\section{\textbf{Education}}
% \vspace{3pt}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    2020 -- now & 
    \textbf{PhD Biology $|$ University of Cambridge} \\
    & \begin{minipage}[t]{\linewidth}
        \begin{itemize}[noitemsep]
            \item PhD in the \href{https://www.lvz.vet.cam.ac.uk/}{\color{teal}Lab of Viral Zoonotics} supervised by Prof. \href{https://www.infectiousdisease.cam.ac.uk/directory/jlh66\%40cam.ac.uk}{\color{teal}Jonathan Heeney}.
            \item Researching computational methods to design broad-spectrum vaccines and antibodies against antigenically diverse pathogens.
            % \item Developed a novel computational method to design broad-spectrum vaccines and applied it to both coronaviruses and influenza viruses.
        \end{itemize}
    \end{minipage} \\
    2015 -- 2018 &
    \textbf{BSc Biology (First Class Honours) $|$ University of Southampton} \\
    & \begin{minipage}[t]{\linewidth}
        \begin{itemize}[noitemsep]
            \item Focused on bioinformatics, with final year project supervised by Dr. \href{https://www.southampton.ac.uk/people/5wycg9/doctor-jane-gibson}{\color{teal}Jane Gibson}.
            \item Scored 86\% in thesis project processing over 1TB of data to identify genetic variants in bladder cancer and used machine learning methods to accurately classify samples.
        \end{itemize}
    \end{minipage}
\end{tabularx}



%----------- RESEARCH -----------

\section{\textbf{Research Internships}}
% \vspace{3pt}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    Oct. 2022 -- & 
    \textbf{Visiting Researcher $|$ Massachusetts Institute of Technology (MIT)} \\
    Jan. 2023 & \begin{minipage}[t]{\linewidth}
        \begin{itemize}[noitemsep]
            \item Evaluated and improved a general‐purpose metagenomics pipeline for the \href{https://naobservatory.org/}{\color{teal}Nucleic Acid Observatory}, a project that aims to build a reliable early detection system for catastrophic biothreats.
            \item Supervised by Prof. \href{https://www.media.mit.edu/people/esvelt/overview/}{\color{teal}Kevin Esvelt} and Dr. Mike McLaren.
        \end{itemize}
    \end{minipage}
\end{tabularx}


%----------- WORK -----------

\section{\textbf{Work Experience}}
\vspace{3pt}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
  2018 -- 2020 & 
  \textbf{Bioinformatician $|$ Lifebit Biotech} \\
  & \begin{minipage}[t]{\linewidth}
      \begin{itemize}[noitemsep]
          \item Joined as employee $\sim$10 shortly after the seed round, and contributed to the company's growth to $\sim$30 employees and \$7.5M series A funding.
          \item Facilitated the end‐to‐end delivery of over seven key projects, including the \href{https://www.genomicsengland.co.uk/news/research-environment-covid-19-lifebit-aws}{\color{teal}Genomics England Research Platform} for COVID‐19 response.
          \item Managed everything from gathering technical requirements to building bioinformatics pipelines and providing professional technical customer support.
          \item Enhanced a robust imputation pipeline, adopted by leading direct-to-consumer genetics firms such as Nebula Genomics and Sano Genetics, for the analysis of data from thousands of customers.
      \end{itemize}
  \end{minipage}
\end{tabularx}



%----------- SERVICE -----------

\section{\textbf{Service}}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    2021 -- now & 
    \textbf{Research Lead of the Cambridge Biosecurity Hub} \\
    & Scaled the society from 0 to 30+ members, helped organise the weekly reading group and mentored two graduate students for a 7-week biosecurity project.
\end{tabularx}


%----------- AWARDS -----------

\section{\textbf{Fellowships and Awards}}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    2020 & 
    \textbf{Doctor of Philosophy Scholarship $|$ Open Philanthropy} \\
    & For three years of PhD studies at the University of Cambridge. \\
    2019 & 
    \textbf{Winner of the world’s first clean meat hackathon $|$ HigherSteaks} \\
    & Prepared and pitched an innovative idea for the use of machine learning to optimise the recycling of cell media, a key factor in reducing costs in cellular agriculture. \\
\end{tabularx}


%----------- SKILLS -----------

\section{\textbf{Programming Skills}}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    \texttt{python} & \textit{Highly competent}: data analysis/visualisation, machine learning, algorithm implementation \\
    \texttt{nextflow} & \textit{Competent}: workflow management, pipeline development \\
    \texttt{R} & \textit{Competent}: data analysis/visualisation \\
    System & \textit{Competent}: Git, Linux, Docker, working with HPC clusters, AWS \\
    Web & \textit{Competent}: HTML5, CSS3, Javascript
\end{tabularx}


%----------- TALKS -----------

\section{\textbf{Talks}}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    2024 &
    \textbf{Covering All Bases: A Novel Method To Design Broad-spectrum Vaccines} \\
    & Presented at the \href{https://www.westcambridgehub.uk/sites/default/files/2024-06/Digital-full-Pandemic\%20research-cafe-programme\%202024.pdf}{\color{teal}Pandemic Preparedness and One Health West Hub Research Cafe}, Cambridge, UK. \\
    2019 & 
    \textbf{Workshop on Nextflow and Containers} \\
    & Prepared and taught a day-long \href{https://github.com/lifebit-ai/jax-tutorial}{\color{teal}workshop} to 45 participants at the Jackson Laboratory, CT, USA. \\
\end{tabularx}

%----------- PUBLICATIONS -----------

\section{\textbf{Publications}}

\subsection*{\textbf{Journal Articles}}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    2022 & 
    \textit{\href{https://doi.org/10.1016/j.celrep.2022.111704}{\color{teal}Myc regulates a pan-cancer network of co-expressed oncogenic splicing factors}} $|$ Cell Reports \\
    & Urbanski L, Brugiolo M, Park S, Angarola BL, Leclair NK, Yurieva M, \textbf{Palmer P}, Sangram S, Olga A. \\
    
    2022 & 
    \textit{\href{https://doi.org/10.3389/fimmu.2022.773982}{\color{teal}Neutralisation Hierarchy of SARS-CoV-2 Variants of Concern Using Standardised, Quantitative Neutralisation Assays Reveals a Correlation With Disease Severity; Towards Deciphering Protective Antibody Thresholds}} $|$ Frontiers in Immunology \\
    & Cantoni D, Mayora-Neto M, Nadesalingam A, Wells DA, Carnell GW, Ohlendorf L, Ferrari M, \textbf{Palmer P}, Chan AC, Smith P, Bentley EM, Einhauser S, Wagner R, Page M, Raddi G, Baxendale H, Castillo-Olivares J, Heeney J, Temperton N. \\
    
    2022 & 
    \textit{\href{https://doi.org/10.3389/fimmu.2021.681636}{\color{teal}AutoPlate: Rapid Dose-Response Curve Analysis for Biological Assays}} $|$ Frontiers in Immunology \\
    & \textbf{Palmer P}, Del Rosario JMM, da Costa KA, Carnell GW, Huang CQ, Heeney JL, Temperton NJ. \\
    
    2021 & 
    \textit{\href{https://doi.org/10.3389/fimmu.2021.748291}{\color{teal}Analysis of serological biomarkers of SARS-COV-2 infection in convalescent samples from severe, moderate and mild covid-19 cases}} $|$ Frontiers in Immunology \\
    & Castillo-Olivares J, Wells DA, Ferrari M, Chan AC, Smith P, Nadesalingam A, Paloniemi M, Carnell GW, Ohlendorf L, Cantoni D, Mayora-Neto M, \textbf{Palmer P}, Tonks P, Temperton NJ, Peterhoff D, Neckermann P, Wagner R, Doffinger R, Kempster S, Otter AD, Semper A, Brooks T, Albecka A, James LC, Page M, Schwaeble W, Baxendale H, Heeney JL. \\
\end{tabularx}

\subsection*{\textbf{Manuscripts in Preparation}}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    2024 & 
    \textit{Covering All Bases: A Computational Method to Design Broad-spectrum T-cell-inducing Vaccines Applied to Betacoronaviruses} $|$ In preparation \\
    & \textbf{Palmer P}, Fedosyuk S, Parthasarathy S, George C, Holbrook J, O'Reilly L, Wiegand L, Carnell GW, Heeney JL and Vishwanath S. \\

    2024 & 
    \textit{A benchmark of deep learning methods for antibody-antigen affinity prediction} $|$ In preparation \\
    & \textbf{Palmer P}, Mathis SV, Del Rosario JMM, Orbegoso CC, Heeney JL, P Liò. \\
\end{tabularx}



%----------- Software -----------

\section{\textbf{Software}}
\vspace{3pt}
\begin{tabularx}{\linewidth}{@{}p{2cm}@{\hspace{5pt}}|@{\hspace{5pt}}X@{}}
    2023 & 
    \textbf{Contributor $|$ \href{https://github.com/nf-core/mag}{\color{teal}nf-core/mag}} (189 stars) \\
    & Nextflow pipeline for assembly and binning of metagenomes. Contribution included the integration of the geNomad tool for enhanced viral classification. \\
    2021 &
    \textbf{Primary Developer $|$ \href{https://github.com/PhilPalmer/AutoPlate}{\color{teal}PhilPalmer/AutoPlate}} (7 stars) \\
    & RShiny app developed to automate the analysis of laboratory assays. Played a crucial role in streamlining COVID-19 and Influenza analyses at the University of Cambridge. \\
    2020 &
    \textbf{Primary Developer $|$ \href{https://github.com/TheJacksonLaboratory/splicing-pipelines-nf}{\color{teal}TheJacksonLaboratory/splicing-pipelines-nf}} (14 stars) \\
    & Development of a Nextflow pipeline for detecting alternative splicing events in RNA-seq data, a collaborative effort with the Olga Anczuków lab at the Jackson Laboratory during tenure at Lifebit. \\
    2020 &
    \textbf{Contributor $|$ \href{https://github.com/apriha/snps}{\color{teal}apriha/snps}} (91 stars) \\
    & Improved a Python package for SNP analysis by identifying and resolving a critical bug in reading 23andMe files, enhancing the package's reliability and user trust. \\
    2018 &
    \textbf{Primary Developer $|$ \href{https://github.com/nf-core/DeepVariant}{\color{teal}nf-core/DeepVariant}} (40 stars) \\
    & Developed a Nextflow pipeline for Google's DeepVariant, using deep neural networks for genetic variant calling from DNA sequencing data. This work marked a significant contribution to the nf-core community during the tenure at Lifebit. \\    
\end{tabularx}



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Basketball, Swimming, Fitness, Eight-ball, Horology}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
